%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document} 

%%%mention the no, time, and venue of the meeting
%%%\noindent The {\em first} Software Engineering Group Project weekly meeting will be held in {\bf Room 2052} at {\bf 11.10am on Friday 9 March 2007}.


\vspace*{15pt}

\begin{center}
\huge \bf Minutes of Client Meeting 4
\end{center}


\begin{center}
\Large \bf Group 13
\end{center}

\begin{center}
\Large \bf Monday 27th August 2012
\end{center}

%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
%%%\section*{Chair}
\section*{Chair}
 Yunyao Yao (a1203525)

\section*{Secretary}
Jun Chen (a1206265)

\section*{Members}
1. Dawei Geng (a1219181)\\
2. Nguyen Khoi (a1187070)\\
3. Yufeng Bai (a1600095)\\
4. Shikai Li (a1214223)\\
5. Yatong Zhou(a1204471)

\vspace*{10pt}

%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section*{Apologies}
None

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Time and Place}
The meeting 4 for the Software Engineering and Project was held in Ingkarni Wardli Building, Room 4.62 at 3:30pm on Monday 27th August 2012.

%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Quorum Announcement}
The chairman announced that a quorum of the group was present, and that the meeting, having been duly convened, was ready to proceed with its topic.

\section{Summary of Previous Meeting}
After the third meeting, the improved movement function of robot has been implement and tested by our group members, the robot move smoothly now. Also our team improved the GUI: Map presenting, Icons and System Log. Moreover, Team has done parts of the SPMP documents at the moment.


\section{Introduction}

\subsection{Current Project Status}
%%%Collect basic functional requirements of {\em Herbs-Online} from diferent stakeholders including the contractor a
Chair  Yunyao Yao gave a presentation of the Risk Management Plan Including ten points:
\begin{itemize} 
\item Team member unable to work
\item Team member leave permanently 
\item Conflict within the team
\item Fail or late of delivery
\item Lack of contribution
\item Project file missing
\item SVN failure
\item Misplacing locker key
\item Damage to the robot
\item Milestone failure
\end{itemize}

\subsection{Client Feedback}
Client gave some suggestions of the SRS draft document and Risk Management plan:
\begin{itemize}
\item Need to use correct language when defining your requirements. (check for the grammatical and spelling errors)
\item The description and rationale often overlap.
\item The source of the requirements should reference minutes from client meetings when applicable.
\item Need to elicit requirements related to handling loss of communication, setting the boundaries of the map and mini map representation.
\item Some user requirements do not reflect clients needs. (Do not require a developer mode and a user mode)
\item Some user requirements need to be decomposed in multiple smaller requirements.
\item Use cases should follow a more complete pass through the system. Also need to consider more alternative paths through the program.
\item We need to use hard figures instead of being vague on Non-functional requirements.
\item For the Risk Management Plan, we need to also think about more technical risks. (like poor understanding of support library)
\end{itemize}

\subsection{Introduction Summary}
\begin{itemize}
\item  Yunyao Yao gave a good presentation to the client. But we need ot add more technical risks. 
\item The SRS document we made is good, but we need to add more details to make it better.
\end{itemize}


\section{Demonstrate the improved manual control}
Our team demonstrated the improved manual control to the client and the feedback is positive. (Good accuracy, turning very right)


\section{Further goal}
Our team will rebuild the robot for better performance, also we will implement the functionality of avoiding walls.

\section{Adjournment}
The next meeting is a group meeting and will be held in Ingkarni Wardli Building, Room 4.62 at 3:30pm on Monday 3rd September 2012.

%%%finally, specifies time of next meeting
\vspace*{10pt}


\end{document}