%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document} 

%%%mention the no, time, and venue of the meeting
%%%\noindent The {\em first} Software Engineering Group Project weekly meeting will be held in {\bf Room 2052} at {\bf 11.10am on Friday 9 March 2007}.


\vspace*{15pt}

\begin{center}
\huge \bf Minutes of Client Meeting 8
\end{center}


\begin{center}
\Large \bf Group 13
\end{center}

\begin{center}
\Large \bf Monday 8th October 2012
\end{center}

%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
%%%\section*{Chair}
\section*{Chair}
Yatong Zhou (a1204471)

\section*{Secretary}
Yunyao Yao (a1203525)

\section*{Members}
1. Dawei Geng (a1219181)\\
2. Yatong Zhou (a1204471)\\
3. Yunyao Yao (a1203525)\\
4. Shikai Li (a1214223)\\
5. Jun Chen (a1206265)\\
6. Nguyen Khoi (a1187070)
\vspace*{10pt}

%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section*{Apologies}
None

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Time and Place}
The 8th meeting for the Software Engineering and Project was held in Ingkarni Wardli Building, Room     4.23 at 3:30pm on Monday 8th October 2012.

%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Quorum Announcement}
The chairman announced that a quorum of the group was present, and that the meeting, having been duly convened, was ready to proceed with its topic.

\section{Summary of Previous Meeting}
1. Shikai Li gave a presentation about the Software Design Document(SDD).\\
2. Dawei Geng demonstrated Milestone 1.\\
3. Client gave us some feedback about Milestone 1.\\


\section{Group Milestone}

\subsection{Introduction}
%%%Collect basic functional requirements of {\em Herbs-Online} from diferent stakeholders including the contractor a
1.Yatong Zhou gave a presentation about the Testing including following points:
\begin{itemize}
\item Stages of testing.
\item Test Model.
\item Testing Tools.
\item Test Plan.
\item Testing Allocation.
\end{itemize}

\subsection{Milestone 2}
\paragraph{} Dawei Geng demonstrated Milestone 2:
\begin{itemize}
\item Auto survey unexpected area.
\item Detect hidden walls and print pixels on the map to represent them.
\item Detect hidden walls during manual control.
\item Keeping away from "no-go" zone.

\end{itemize}

\subsection{Client Feedback}
1. Client suggested that we should let the person who did not write the code to test it, so the tests can be done without any assumptions.\\
2. Client told us that whatever functions we wrote in Milestone, we should be able to demonstrate it.\\
3. Client highly suggested that we should add an instant stop mechanism to stop the automatic mode anytime and switch to manual mode.\\
4. Client suggested we make the automatic scanning process faster.


\subsection{Further goal}
1. Finish unimplemented functions of the robot and GUI.\\
2. Improve the software according to client's suggestions.\\
3. Make a test plan and begin testing. \\
%%%more issues should make it like the above one.

\section{Adjournment}
The next meeting is a group meeting and will be held in Ingkarni Wardli Building, Room 4.23 at 3:30pm on Monday 15th October 2012.

%%%finally, specifies time of next meeting
\vspace*{10pt}


\end{document}