%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document} 

%%%mention the no, time, and venue of the meeting
%%%\noindent The {\em first} Software Engineering Group Project weekly meeting will be held in {\bf Room 2052} at {\bf 11.10am on Friday 9 March 2007}.


\vspace*{15pt}

\begin{center}
\huge \bf Minutes of Client Meeting 1
\end{center}


\begin{center}
\Large \bf Group 13
\end{center}

\begin{center}
\Large \bf Monday 6th August 2012
\end{center}

%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
%%%\section*{Chair}
\section*{Chair}
 Dawei Geng (a1219181)

\section*{Secretary}
Yufeng Bai (a1600095)

\section*{Members}
1. Nguyen Khoi (a1187070)\\
2. Yatong Zhou (a1204471)\\
3. Yunyao Yao (a1203525)\\
4. Shikai Li (a1214223)\\
5. Jun Chen (a1206265)
\vspace*{10pt}

%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section*{Apologies}
None

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Time and Place}
The first meeting for the Software Engineering and Project was held in Ingkarni Wardli Building, Room     4.23 at 3:30pm on Monday 6th August 2012.

%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Quorum Announcement}
The chairman announced that a quorum of the group was present, and that the meeting, having been duly convened, was ready to proceed with its topic.

\section{Summary of Previous Meeting}
This is the first meeting.

\section{Group Milestone}

\subsection{Introduction}
%%%Collect basic functional requirements of {\em Herbs-Online} from diferent stakeholders including the contractor a
1. Chair David gave the presentation about the content of the poster which we made last week, including the name and the main position of each group member.\\
2. Each group member give a brief introduction about himself including the name, major and advantages

\subsection{client requirement}
1. the robot can not walk out of map.\\
2. we need to keep tracking and avoid block.\\
3. robot walk in normal speed, when the sensor detect the wall, robot will slow down.\\
4. robot can not push the wall and colliding is not permitted. \\
5. robot should find the starting position. \\
6. software should support the bigger map. For this project, we need to operate the robot in fixed size(less than A1)\\
7. if robot run out of power, it will go back to where it start.\\
8. robot is not allowed to damage.\\
9. power saving module is better(optional).\\
10. It is better if the robot can find the shortest way to reach destination(optional).\\
11. We need to save and load map. \\
12. the robot should implements the manual and automatic control.

\subsection{notification}
1. Client give us the lock key and the robot module.\\ 
2. Topic is presented in CS forum, choosing one topic for next meeting.\\
3. Everyone has the chance to be the chair.\\

\section{Individual Milestone Report}
none


\section{Project Administration}
none


%%%more issues should make it like the above one.
\section{Requirements Elicitation}
none

\section{Adjournment}
The next meeting is a group meeting and will be held in Ingkarni Wardli Building, Room 4.23 at 3:30pm on Monday 13th August 2012.

%%%finally, specifies time of next meeting
\vspace*{10pt}


\end{document}