%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document} 

%%%mention the no, time, and venue of the meeting
%%%\noindent The {\em first} Software Engineering Group Project weekly meeting will be held in {\bf Room 2052} at {\bf 11.10am on Friday 9 March 2007}.


\vspace*{15pt}

\begin{center}
\huge \bf Minutes of the Sixth Internal Meeting
\end{center}


\begin{center}
\Large \bf Group 13
\end{center}

\begin{center}
\Large \bf  Saturday 29th September 2012
\end{center}

%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
%%%\section*{Chair}
\section*{Chair}
 Dawei Geng (a1219181)

\section*{Secretary}
Yufeng Bai (a1600095)

\section*{Members}
1. Nguyen Khoi (a1187070)\\
2. Yatong Zhou (a1204471)\\
3. Yunyao Yao (a1203525)\\
4. Shikai Li (a1214223)\\
5. Jun Chen (a1206265)\\
6. Yunyao Yao (a1203525)
\vspace*{10pt}

%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section*{Apologies}
None

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Time and Place}
The Fifth meeting for the Software Engineering and Project was held in Ingkarni Wardli Building, Room 4.23 at 2:00pm on Saturday 29th September 2012.


%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Quorum Announcement}
The chairman announced that a quorum of the group was present, and that the meeting, having been duly convened, was ready to proceed with its topic.

\section{Summary of Previous Meeting}
\begin{enumerate}
\item Build the XML map.
\item Build the Panel Board.
\item Implement path finding function.
\end{enumerate}
 

\section{The GUI Improvement}
\begin{enumerate}
\item Improve the GUI  to allow the map size to be defined by user. 
\item Improve the GUI to allow the robot's start position to be defined by user, and the icon of the robot is able to be demonstrated on the map. 
\item The movement of the icon of robot is able to be controlled by the direction arrows.
\end{enumerate}

\section{Path finding}

\begin{enumerate}
\item Complete the "set path" function and make sure this function work correctly.
\item Write the thread to attempt to connect the robot with GUI.
\item Improve the movement of the robot to make sure it scans the pixel properly.

\end{enumerate}    

\section{Adjournment}
The next meeting is a group meeting and will be held in Ingkarni Wardli Building, Room 4.23 on Week 9 2012.

%%%finally, specifies time of next meeting
\vspace*{10pt}


\end{document}
