%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document} 

%%%mention the no, time, and venue of the meeting
%%%\noindent The {\em first} Software Engineering Group Project weekly meeting will be held in {\bf Room 2052} at {\bf 11.10am on Friday 9 March 2007}.


\vspace*{15pt}

\begin{center}
\huge \bf Minutes of the Fifth Internal Meeting
\end{center}


\begin{center}
\Large \bf Group 13
\end{center}

\begin{center}
\Large \bf  Wednesday 26th September 2012
\end{center}

%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
%%%\section*{Chair}
\section*{Chair}
 Dawei Geng (a1219181)

\section*{Secretary}
Yufeng Bai (a1600095)

\section*{Members}
1. Nguyen Khoi (a1187070)\\
2. Yatong Zhou (a1204471)\\
3. Yunyao Yao (a1203525)\\
4. Shikai Li (a1214223)\\
5. Jun Chen (a1206265)\\
6. Yunyao Yao (a1203525)
\vspace*{10pt}

%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section*{Apologies}
None

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Time and Place}
The Fifth meeting for the Software Engineering and Project was held in Ingkarni Wardli Building, Room 4.23 at 2:00pm on Wednesday 26th September 2012.


%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Quorum Announcement}
The chairman announced that a quorum of the group was present, and that the meeting, having been duly convened, was ready to proceed with its topic.

\section{Summary of Previous Meeting}
\begin{enumerate}
\item Analysing the documents we have finished so far.
\item Analysing the program we have finished so far.
\item Demonstrating the function of the robot so far.
\item Set the further goal.
\end{enumerate}
 

\section{The Map Building}
\begin{enumerate}
\item Write the java codes to build map in XML file, includes five java files: Map, Pixel, Test, XMLDocument and XMLReaderWriter. These files have already updated to SVN repository.

\item Write the java codes to build the Panel Board and the red dot, which are used to demonstrate the movement of the robot. The map of GUI is built by a lot of pixels(grids), when robot traverses one pixel, the pixel will be marked by another colour.

\end{enumerate}

\section{Path finding}
\begin{enumerate}
\item Using Depth First Search to traverse all pixels in the map. The robot decides whether the robot finish the traverse or not according to the return value of the DFS.

\item Using PathFinder function to find the path from the current position to next position.

\item Using findNearestUnexplorePixel function to find the nearest unexplored pixel when the 4 directions(east, west, north, south) of the current position have already explored.
\item Using Robot Scanner class to decide when and how the robot moves.

\end{enumerate}    

\section{Adjournment}
The next meeting is a group meeting and will be held in Ingkarni Wardli Building, Room 4.23 at 3:30pm on Week 9 2012.

%%%finally, specifies time of next meeting
\vspace*{10pt}


\end{document}
