%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document} 

%%%mention the no, time, and venue of the meeting
%%%\noindent The {\em first} Software Engineering Group Project weekly meeting will be held in {\bf Room 2052} at {\bf 11.10am on Friday 9 March 2007}.


\vspace*{15pt}

\begin{center}
\huge \bf Minutes of Client Meeting 7
\end{center}


\begin{center}
\Large \bf Group 13
\end{center}

\begin{center}
\Large \bf Friday 5th October 2012
\end{center}

%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
%%%\section*{Chair}
\section*{Chair}
Shikai Li (a1214223)

\section*{Secretary}
Yunyao Yao (a1203525)

\section*{Members}
1. Dawei Geng (a1219181)\\
2. Yatong Zhou (a1204471)\\
3. Yunyao Yao (a1203525)\\
4. Shikai Li (a1214223)\\
5. Jun Chen (a1206265)\\
\vspace*{10pt}

%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section*{Apologies}
None

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Time and Place}
The 7th meeting for the Software Engineering and Project was held in Ingkarni Wardli Building, Room     4.23 at 1:00pm on Friday 5th October 2012.

%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Quorum Announcement}
The chairman announced that a quorum of the group was present, and that the meeting, having been duly convened, was ready to proceed with its topic.

\section{Summary of Previous Meeting}
1. Nguyen Khoi gave a presentation about the Configuration Management and Quality Process Assessment.\\
2. Dawei Geng demonstrated some improvement about the robot.\\


\section{Group Milestone}

\subsection{Introduction}
%%%Collect basic functional requirements of {\em Herbs-Online} from diferent stakeholders including the contractor a
1.Shikai Li gave a presentation about the Software Design Document(SDD) including following points:
\begin{itemize}
\item System Architecture and Components Design.
\item Data Design.
\item Diagram Design.
\item Resources Estimates.
\item Milestone Overview.
\end{itemize}

\subsection{Milestone 1}
\paragraph 1. Shikai Li and Yatong Zhou demonstrated GUI part of Milestone 1:
\begin{itemize}
\item Map Creating, Loading and Saving.
\item Control buttons can move the robot icon(represented as an small arrow) on the map and mark the path as green colour.
\item Obstacle, Hidden Wall, Unexplored Area, Buffer Zone, No-go Zone are marked as different colours.
\item Bluetooth connection implemented as well as battery display.
\item Speed control and coordinate implemented.
\end{itemize}

\paragraph 2. Dawei Geng demonstrated Robot part of Milestone 1:
\begin{itemize}
\item Robot will stop when facing walls.
\item Mapping walls. 
\item Display walls.
\end{itemize}

\subsection{Client Feedback}
1. Client suggested that we should be able to implement No-go zone setting by mouse clicking.\\
2. Client agreed that we do not need developer mode.\\
3. Client said we need files management in our file repository, such as makefile or file rebuild.\\
4. Client required us to write a map files reader that can read XML files with DTD.\\

\subsection{Further goal}
1. Finish unimplemented functions in Milestone 1\\
2. Push to Milestone 2\\
3. Make a test plan and begin testing after Milestone 2\\
%%%more issues should make it like the above one.

\section{Adjournment}
The next meeting is a group meeting and will be held in Ingkarni Wardli Building, Room 4.23 at 3:30pm on Monday 8th October 2012.

%%%finally, specifies time of next meeting
\vspace*{10pt}


\end{document}