%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document}

%%%mention the no, time, and venue of the meeting
%%%\noindent The {\em first} Software Engineering Group Project weekly meeting will be held in {\bf Room 2052} at {\bf 11.10am on Friday 9 March 2007}.


\vspace*{15pt}

\begin{center}
\huge \bf Minutes of Client Meeting 5
\end{center}


\begin{center}
\Large \bf Group 13
\end{center}

\begin{center}
\Large \bf Monday 3rd September 2012
\end{center}

%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
%%%\section*{Chair}
\section*{Chair}
 Dawei Geng (a1203525)

\section*{Secretary}
Shikai Li (a1206265)

\section*{Members}

1. Nguyen Khoi (a1187070)\\
2. Yufeng Bai (a1600095)\\
3. Yunyao Yao (a1203525)\\
4. Yatong Zhou(a1204471)\\
5. Jun Chen (a1206265)
\vspace*{10pt}

%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section*{Apologies}
None

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Time and Place}
The meeting 5 for the Software Engineering and Project was held in Ingkarni Wardli Building, Room 4.62 at 3:30pm on Monday 3rd September 2012.

%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Quorum Announcement}
The chairman announced that a quorum of the group was present, and that the meeting, having been duly convened, was ready to proceed with its topic.

\section{Summary of Previous Meeting}
After the fourth meeting, we synchronizing the robot movement to make the robot move more accurate. Improved manual control. And finished SPMP documents.



\section{Introduction}

\subsection{Current Project Status}
%%%Collect basic functional requirements of {\em Herbs-Online} from diferent stakeholders including the contractor a
Chen Jun gave a presentation of the Software Project Management Plan(SPMP) Including ten points:
\begin{itemize}
\item Propose of SPMP
\item Plan should reaction of any situation
\item Explain each component of SPMP Document
\item Give the definition of terminology and abbreviation are used in this project
\item How project organized, include how tasks are assigned to each member and risk management
\item Use waterfall model for this project
\item Work activity
\item Milestone
\item Version control tool: SVN
\item Project Char
\end{itemize}

\subsection{Client Feedback}
Client has asked some Question of current project:
\begin{itemize}
\item Q: How works are assigned to each member? \\
      A: Base on the strength of each member.
\item Q: What is the current schedule of project?\\
      A: Show the client control the robot via mini GUI through Button.
\item Q: Task of this week?\\
      A: Implement ultrasonic wave sensor on Robot
\item Chair ask the client when is the end of second mile stone. Reply is the end of this semester.
\item Multi threat is not necessary in this project.
\item Peer assessment is still under discussion
\end{itemize}

\subsection{Introduction Summary}
\begin{itemize}
\item  Chen Jun give a presentation of Software Project Management Plan(SPMP).
\end{itemize}


\section{Demonstrate manual control through}
Our team demonstrated to client manual control via GUI and the feedback is positive. (Good accuracy, turning very right)


\section{Further goal}
Our team will finish UML Diagram design and then complete Software Design Document.

\section{Adjournment}
The next meeting is a group meeting and will be held in Ingkarni Wardli Building, Room 4.62 at 3:30pm on Monday 10th September 2012.

%%%finally, specifies time of next meeting
\vspace*{10pt}


\end{document}
