%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document} 

%%%mention the no, time, and venue of the meeting
%%%\noindent The {\em first} Software Engineering Group Project weekly meeting will be held in {\bf Room 2052} at {\bf 11.10am on Friday 9 March 2007}.


\vspace*{15pt}

\begin{center}
\huge \bf Minutes of the Third Internal Meeting
\end{center}


\begin{center}
\Large \bf Group 13
\end{center}

\begin{center}
\Large \bf Monday 9th August 2012
\end{center}

%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
%%%\section*{Chair}
\section*{Chair}
 Dawei Geng (a1219181)

\section*{Secretary}
Yufeng Bai (a1600095)

\section*{Members}
1. Nguyen Khoi (a1187070)\\
2. Yatong Zhou (a1204471)\\
3. Yunyao Yao (a1203525)\\
4. Shikai Li (a1214223)\\
5. Jun Chen (a1206265)\\
6. Yunyao Yao (a1203525)
\vspace*{10pt}

%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section*{Apologies}
None

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Time and Place}
The second meeting for the Software Engineering and Project was held in Ingkarni Wardli Building, Room 4.23 at 2:00pm on Friday 31st August 2012.

%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Quorum Announcement}
The chairman announced that a quorum of the group was present, and that the meeting, having been duly convened, was ready to proceed with its topic.

\section{Summary of Previous Meeting}
1. The presentation of Risk Management.\\
2. Get the feedback from client about SRS. \\
3. Demonstrate the improved manual control.\\
4. Set the further goal.\\
 

\section{Group Milestone}

\subsection{discussion}
%%%Collect basic functional requirements of {\em Herbs-Online} from diferent stakeholders including the contractor a
1. We need to work on Software Design Document.\\
2. We need to set the smart robot milestone 1 based on project gantt chart.\\
3. We need to finish improving graphic user interface.\\



\subsection{Physical Design}
1. Put the sensor on the robot and make sure theses sensors are working properly.

\subsection{Code Design And Test}
1. The GUI progress: improve the GUI icons according to client's opinion and change the colour of button to green according to client's requirements.\\
2. Fix the manual control operation and make sure the manual control to work on GUI demo correctly. For our designing, the developer builds six buttons on GUI: forward, backward, left-rotating, right-rotating, turn left 90 angles and turn right 90 angles. \\

\section{Milestone Report}
1. Discuss the next week's milestone

\section{Documents}
1. Fix the SRS report based on client's feedback.\\
2. Keep working on  the report of the SPMP.\\
3. Discuss the Software Design Document. 


\section{Project Administration}
1. Put the SRS feedback in folder.


%%%more issues should make it like the above one.
\section{Requirements Elicitation}
1. the colour of arrow on GUI .\\
2. the spelling error to check.\\
3. The Sensor to implement the checking hidden wall and external object.\\  

\section{Adjournment}
The next meeting is a group meeting and will be held in Ingkarni Wardli Building, Room 4.23 at 3:30pm on Monday 3rd September 2012.

%%%finally, specifies time of next meeting
\vspace*{10pt}


\end{document}
