%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 25 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document}

%%%mention the no, time, and venue of the meeting
\noindent Software Engineering Group Project internal meeting 4 will be held in {\bf Room 462} at {\bf 3.30pm on 27 August 2012}.


\vspace*{15pt}

\begin{center}
\huge \bf Agenda \\Client Meeting 4
\end{center}



%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
\section*{Chair: Yunyao Yao (a1203525)}
\section*{Present}
\begin{enumerate}
\item Yufeng Bai (a1600095)
\item Yatong Zhou(a1204471)
\item Nguyen Khoi (a1187070)
\item Dawei Geng (a1219181)
\item Shikai (a1214223)
\item Jun Chen (a1206265)
\end{enumerate}
%\vspace*{10pt}
%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section{Apologies}

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Presentation}
The Risk Management Plan presented by Yaoyun Yao.

\section{SRS Feedback}
Team members gathering feedback form the client about the SRS. 
%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Project Status}

\subsection{Current Status}
The current progress will be introduced. Collecting suggestion from client.
\begin{enumerate}
	\item The GUI Improvement and Completion: Map presenting, Icons, and System Log.
	\item Manual control over main GUI.
\end{enumerate}
\subsection{Future Goal}
The goal of next week will be rebuild the robot and implementing the functionality of avoiding walls. (Smart Robot Milestone 1 as the project plan)

\section{Milestone Freeze}
The first milestone's forum will be presented to the client, and currently progress of it will be introduced.
\subsection{Questions About the Milestone}
Team members ask questions about first milestones. 
\begin{enumerate}
	\item  When the program will be frozen?
	\item  When is the presentation of the first milestone?
\end{enumerate}

\section{Other Questions}
Other project-related questions will be asked. Including: 
\begin{enumerate}
	\item  Is it necessary for every team member work on the same documenting or programming job at the same time?
	\item  Feedback of the possible solutions the team had so far to the Motors' asynchronous stopping problem.
\end{enumerate}



%%%finally, specifies time of next meeting
\vspace*{10pt}
\noindent Note: Next meeting to be held on 03 September 2012.


\end{document}
