%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 25 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document}

%%%mention the no, time, and venue of the meeting
\noindent The Software Engineering Group Project internal meeting 4 will be held in {\bf Room 462} at {\bf 3.30pm on 14 September 2012}.


\vspace*{15pt}

\begin{center}
\huge \bf Agenda \\Internal Meeting 4
\end{center}



%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
\section*{Chair: Dawei Geng(a1219181)}
\section*{Present}
\begin{enumerate}
\item Yufeng Bai (a1600095)
\item Nguyen Khoi (a1187070)
\item Yatong Zhou (a1204471)
\item Yunyao Yao (a1203525)
\item Shikai (a1214223)
\item Jun Chen (a1206265)
\end{enumerate}
%\vspace*{10pt}
%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section{Apologies}
None.

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Document Review}
The documents made so far will be reviewed, this section will held by Yufeng Bai, the documentation manager.

\section{Code Review}
Code reviewing will held by Nguyen Khoi, the main developer and QA manager.

%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Current project status}
Team members will report their progresses. Including:
\begin{enumerate}
	\item  Blue-tooth connection protocol improved, now can handle both auto \& manual command.
	\item  Software code skeleton completed.
	\item  GUI update.
\end{enumerate}


\section{Next weeks project plan}
From next week the project will officially enter implementation phase, next week the team will focus on implementing milestone 1.


\section{SVN Repository}
%%%if there are more sub-issues, make them as subsections.
The structure of the team's SVN repository will be reconstruct to fix future developing need:
The "Code" folder will have three part each contains a working copy of the software, versions of software updates, and program parts that team members' are currently working on. 
The "Document" folder will contain agendas, minutes, and other documents which requires team members working together, such document will be divided in to "Drafts" and "Final" folder, contains drafts of updates and the final versions which pulled from drafts. 

%%%more issues should make it like the above one.
\section{\LaTeX{} Editor}
Sublime Text 2 with \LaTeX{} plug-in will be introduced to team members, and further work of documents will be based on this tool to prevent \LaTeX{} file format errors. 

\section{Questions Discuss}
%%%if there are more subissues, make them as subsections.
Questions that team members had so far will be discussed.

%%%more issues should make it like the above one.
\section{Next Client Meeting's Topic}
Topic and Chair of next meeting. Question collection for next meeting. 

%%%finally, specifies time of next meeting
\vspace*{10pt}
\noindent Note: Next meeting to be held on next week.


\end{document}
