%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 25 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document}

%%%mention the no, time, and venue of the meeting
\noindent Software Engineering Group Project internal meeting 7 will be held in {\bf Room 462} at {\bf 3.30 pm on Week 9 2012}.


\vspace*{15pt}

\begin{center}
\huge \bf Agenda \\Client Meeting 7
\end{center}



%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
\section*{Chair:Shikai Li (a1214223)}
\section*{Present}
\begin{enumerate}
\item Yufeng Bai (a1600095)
\item Yatong Zhou(a1204471)
\item Yunyao Yao (a1203525)
\item Jun Chen (a1206265)
\item Dawei Geng (a1219181)
\item Nguyen Khoi (a1187070)
\end{enumerate}
%\vspace*{10pt}
%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section{Apologies}

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Presentation}
The Software Design Document Presentation by Shikai Li.

%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{SDD Critique}
Getting feedback of the Software Design Document from client. 

\section{The 1st Group Milestone}
\begin{enumerate}
\item The achievement of the 1st Group Milestone is demonstrated according to the Milestone 1 sheet by Dawei Geng and Shikai Li.
\item Dawei Geng mainly takes responsibility of the robot part. 
\item Shikai Li mainly takes responsibility of the GUI part.  
\end{enumerate}

\section{The mystery presentation topic}
Negotiate with the client to determine the topic of the mystery presentation.

\section{The progress report}
Negotiate with the client to determine the requirement and the template of the progress report.   

\section{Future Goal}
The future plan for the team is complete the Smart Robot Milestone 2 (Group milestone 2).

\section{Other Technical Questions}
Other project-related questions will be asked.



%%%finally, specifies time of next meeting
\vspace*{10pt}
\noindent Note: Next meeting to be held on week 10.


\end{document}
