%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 25 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document}

%%%mention the no, time, and venue of the meeting
\noindent Software Engineering Group Project internal meeting 3 will be held in {\bf Room 462} at {\bf 3.30pm on 20 August 2012}.


\vspace*{15pt}

\begin{center}
\huge \bf Agenda \\Client Meeting 3
\end{center}



%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
\section*{Chair: Yufeng Bai (a1600095)}
\section*{Present}
\begin{enumerate}
\item Yatong Zhou(a1204471)
\item Nguyen Khoi (a1187070)
\item Dawei Geng (a1219181)
\item Yunyao Yao (a1203525)
\item Shikai (a1214223)
\item Jun Chen (a1206265)
\end{enumerate}
%\vspace*{10pt}
%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section{Apologies}

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Presentation}
The SRS first draft will be present to the client.

%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Project Status}

\subsection{Current Status}
The current progress will be introduced. Collecting suggestion from client.
\begin{enumerate}
\item The GUI overview: the prototype GUI will be shown to the client, including dialog windows.
\item Robot movement demonstration: basic movement of the robot will be shown to the client.
\item Manual control through Bluetooth demonstration: we are now be able to manual control the robot through the keyboard of the host machine. 
\end{enumerate}
\subsection{Future Goal}
The goal until next week's meeting will be introduced. 



\section{Milestone Negotiation}
%%%if there are more subissues, make them as subsections.
\subsection{Project Gantt Chart}
The project's gantt chart will be shown to the client and collecting feedback form the client. 
\subsection{Priority of the Milestones}
Discuss with client to initial a plan for the first milestones implementation. For now the functionalities we are planning to implement in the first milestone are:

\textbf{GUI Milestone: }
\begin{enumerate}
\item Map creation and display one the GUI.
\item Objects' representation. (i.e.: map, walls, hidden walls, and robot)
\item System log display.
\item Handle connection loss.
\end{enumerate}

\textbf{Smart Robot Milestone: }
\begin{enumerate}
\item Robot stops when facing a wall, and send message to the hos machine.
\end{enumerate}

\textbf{Advanced Topic: }
\begin{enumerate}
\item Robot be able to safely travel within to map and avoid walls.
\item Robot mapping a long wall.
\item Robot mapping a corner of the walls. 
\end{enumerate}

\subsection{Questions About the Milestone}
Team members ask questions about first milestones. 

%%%finally, specifies time of next meeting
\vspace*{10pt}
\noindent Note: Next meeting to be held on 27 August 2012.


\end{document}
