%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 25 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document}

%%%mention the no, time, and venue of the meeting
\noindent The Software Engineering Group Project internal meeting 3 will be held in {\bf Room 462} at {\bf 3.30pm on 31 August 2012}.


\vspace*{15pt}

\begin{center}
\huge \bf Agenda \\Internal Meeting 3
\end{center}



%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
\section*{Chair: Dawei Geng(a1219181)}
\section*{Present}
\begin{enumerate}
\item Yufeng Bai (a1600095)
\item Nguyen Khoi (a1187070)
\item Yatong Zhou (a1204471)
\item Yunyao Yao (a1203525)
\item Shikai (a1214223)
\item Jun Chen (a1206265)
\end{enumerate}
%\vspace*{10pt}
%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section{Apologies}
None.

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Document Review}
The documents made so far will be reviewed, this section will held by Yufeng Bai, the documentation manager.

\section{Code Review}
Code reviewing will held by Nguyen Khoi, the main developer and QA manager.

%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Current project status}
Team members will report their progresses. Including:
\begin{enumerate}
	\item  The graphic user interface progress: improved GUI icons, button color changed.
	\item  Manual Control from GUI demo.
	\item  SPMP progress report.
\end{enumerate}


\section{Next weeks project plan}
Establish the next weeks milestones based on current progress. Ideally, next week the team will be working on:  
\begin{enumerate}
	\item SDD(Software Design Document).
	\item Smart Robot Milestone 1 based on project gantt chart. 
	\item Finishing improving graphic user interface.
\end{enumerate}

\section{Questions Discuss}
%%%if there are more subissues, make them as subsections.
Questions that team members had so far will be discussed.

%%%more issues should make it like the above one.
\section{Next Client Meeting's Topic}
Topic and Chair of next meeting. Question collection for next meeting. 

%%%finally, specifies time of next meeting
\vspace*{10pt}
\noindent Note: Next meeting to be held on 09 September 2012.


\end{document}
