%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 25 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document}

%%%mention the no, time, and venue of the meeting
\noindent The Software Engineering Group Project internal meeting 1 will be held in {\bf Room 462} at {\bf 3.30pm on 9 August 2012}.


\vspace*{15pt}

\begin{center}
\huge \bf Agenda \\Internal Meeting 1
\end{center}



%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
\section*{Chair: Dawei Geng(a1219181)}
\section*{Present}
\begin{enumerate}
\item Yufeng Bai (a1600095)
\item Nguyen Khoi (a1187070)
\item Yatong Zhou (a1204471)
\item Yunyao Yao (a1203525)
\item Shikai (a1214223)
\item Jun Chen (a1206265)
\end{enumerate}
%\vspace*{10pt}
%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section{Apologies}

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Presentation}
None

%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Rebuild the Robot}
Rebuild the robot to fit the purpose of the current project. Remove the unwanted part. Set up all the sensors in correct locations. 
\section{Initial functionality realization}
Realize a few functionality of the project. 
\begin{enumerate}
\item Connect the robot with PC through Bluetooth.
\item Allow robot to move around. 
\item When obstructions appears, the robot will stops. 
\end{enumerate}

\section{Further Project Requirements Elicitation Plan}
%%%if there are more subissues, make them as subsections.
Further requirements elicitation within the team. 
\begin{enumerate}

\item Elicit Functional Requirements

\item Elicit Design Requirements

\item Elicit Implementation Requirements

\end{enumerate}



%%%more issues should make it like the above one.
\section{Next Meeting with Client}
Topic and Chair of next meeting. Question collection for next meeting. 

%%%finally, specifies time of next meeting
\vspace*{10pt}
\noindent Note: Next meeting to be held on 13 August 2012.


\end{document}
