%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 25 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document}

%%%mention the no, time, and venue of the meeting
\noindent Software Engineering Group Project internal meeting 6 will be held in {\bf Room 462} at {\bf 3.30 pm on 10 September 2012}.


\vspace*{15pt}

\begin{center}
\huge \bf Agenda \\Client Meeting 6
\end{center}



%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
\section*{Chair:Nguyen Khoi (a1187070)}
\section*{Present}
\begin{enumerate}
\item Yufeng Bai (a1600095)
\item Yatong Zhou(a1204471)
\item Yunyao Yao (a1203525)
\item Jun Chen (a1206265)
\item Dawei Geng (a1219181)
\item Shikai Li (a1214223)
\end{enumerate}
%\vspace*{10pt}
%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section{Apologies}

%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Presentation}
The Configuration Management and Quality Process Assessment presentation by Nguyen Khoi.

%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{SPMP Critique}
Getting feedback of the SPMP from client. 

\section{Project Status}

\subsection{SDD Document}
The Software Design Document progress and the software overall design will be presented to client, and feedback will be gathered.

\subsection{Current Status}
\begin{enumerate}
	\item Bluetooth connection protocol improved. 
	\item Threads implementation on robot to monitor the sensor.
	\item Transfer sensor between host and robot.
	\item Simple avoid action when moving forward. 
\end{enumerate}
\subsection{Future Goal}
The future plan for the team is complete the Smart Robot Milestone 1 (Group milestone 1).

\section{Other Technical Questions}
Other project-related questions will be asked.



%%%finally, specifies time of next meeting
\vspace*{10pt}
\noindent Note: Next meeting to be held after the middle break.


\end{document}
